COG-ED Manuscript

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
changed fig location and caption

```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back."}

@@

`r Figure2`
*Supplementary Figure 1* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.

`r Figure3`
*Supplementary Figure 2* Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity.

@@

`r Figure2`
*Supplementary Figure 1* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.

Johnson-Neyman intervals:

@@

`r Figure3`
*Supplementary Figure 2* Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity.

>>>>

```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back."}

@@

@@

```{r FigHyp2c, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation."}

interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = T, point.shape = T,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = T) + theme_apa() +
scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
```
Johnson-Neyman intervals:

@@

```{r Fig2cSA and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity."}

  ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
```
